Collective behavior of Suspended Janus Particles via an Integral Equation Method

### 2022-05-10 doc/PRF2022/PRF_main.tex
update

@@

>>>>

\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{shear_0.png}
  \includegraphics[width=0.4\textwidth]{shear_1000.png}\\
  \includegraphics[width=0.4\textwidth]{shear_2000.png}
    \includegraphics[width=0.4\textwidth]{shear_dist.jpg}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:shear_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a shear flow when $\dot\gamma=0.05$. }
\end{figure}

\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{shear_checker_0.png}
  \includegraphics[width=0.4\textwidth]{shear_checker_250.png}\\
  \includegraphics[width=0.4\textwidth]{shear_checker_500.png}
    \includegraphics[width=0.4\textwidth]{shear_checker_750.png}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:shear_2} Snapshots of simulation using boundary condition \eqref{eq:bcs}(c) in a shear flow when $\dot\gamma=0.15$. }
\end{figure}

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{TG_0.png}
  \includegraphics[width=0.4\textwidth]{TG_2500.png}\\
  \includegraphics[width=0.4\textwidth]{TG_5000.png}
    \includegraphics[width=0.4\textwidth]{TG_dist.jpg}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:TG_1} Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a Taylor-Green flow when $V_0=0.1$ and $l=0.5$.}
\end{figure}
